### 2022-03-21 paper/localpsf.tex
about to remove old stuff from paper

Since our end goal is constructing an H-matrix, we are freed from strict adherence to the PC format. This allows us to modify the PC approach to address well-known deficiencies. PC approximations are based on an assumption of local translation invariance \cite{LOCATRANSLATIONINVARIANCE}, while our method is based on an assumption that we call ``normalized local mean displacement invariance,'' which is more general than local translation invariance, and includes both low rank approximation and local translation invariance as special cases (see Section \ref{sec:local_mean_displacement_invariance}). PC approximations have well-known issues near boundaries called boundary artifacts, which are caused by the boundary artificially ``cutting off'' impulse responses. 
%One must extend the impulse responses outside of the domain where they are undefined, but
%. Various extension techniques have been used, such as extension by zero, and reflection across the boundary, yet 
%no known extension technique is fully satisfactory \cite{BOUNDARYETENSION}. 
In our method we do not have an issue with boundary artifacts because we temporarily exclude impulse responses from the approximation procedure whenever the approximation procedure attempts to evaluate the impulse response at a location where it is undefined. Our approximation cannot be written as a weighted sum of convolution operators, so we cannot apply our approximation to vectors via the FFT. This is fine because our approximation is an H-matrix, which can be applied to vectors even faster.

>>>>

Since our end goal is constructing an H-matrix, we are freed from strict adherence to the PC format. This allows us to modify the PC approach to address well-known deficiencies. PC approximations are based on an assumption of local translation invariance \cite{LOCATRANSLATIONINVARIANCE}, while our method is based on an assumption that we call ``normalized local mean displacement invariance,'' which is more general than local translation invariance, and includes both low rank approximation and local translation invariance as special cases (see Section \ref{sec:local_mean_displacement_invariance}). PC approximations have well-known issues near boundaries called boundary artifacts, which are caused by the boundary artificially ``cutting off'' impulse responses. 
%One must extend the impulse responses outside of the domain where they are undefined, but
%. Various extension techniques have been used, such as extension by zero, and reflection across the boundary, yet 
%no known extension technique is fully satisfactory \cite{BOUNDARYETENSION}. 
In our method we do not have an issue with boundary artifacts because we temporarily exclude impulse responses from the approximation procedure whenever the approximation procedure attempts to evaluate the impulse response at a location where it is undefined. In exchange for these benefits, our approximation cannot be written as a weighted sum of convolution operators, so we cannot apply our approximation to vectors via the FFT. This is fine because our approximation is an H-matrix, which can be applied to vectors even faster.
